---
title: "Predicting League of Legends Win rate"
date: October, 2022
---

# Introduction


# Dataset
[Provider](https://www.kaggle.com/datasets/junhachoi/all-ranked-solo-games-on-kr-server-24-hours?select=sat+df.csv)

# Prepare all the package
```{r}
library(tidyverse)
library(tidymodels)
library(corrplot)
library(discrim)
library(poissonreg)
library(corrr)
library(klaR)
library(vroom)
tidymodels_prefer()
```

# Exploratory Data analysis
## Pre EDA
As the author of the dataset suggests, the orginal encoding is cp949 (korean encoding). So it is wise to convert it to UTF-8 first to avoid encoding issue

Here I use the `iconv` command line tool to change the encoding
```bash
iconv -f cp949 -t utf-8 league_data.csv > league_data_utf8.csv
```

## Explaination of variables in the dataset
Variables of interest
- KoreanTime: local game time in UTC+9
- championName: factor ()
- championRole

Variables of interest that cannot be fully determined during game preparation stage 
- teamId: 100 (blue team), 200 (red team), system randomly assigned team id. since the game map is not entirely symmetrical, blue and team have some minor differences.
- gameEndedInEarlySurrender: True/False, indicating if one team surrendered before 20 minutes
- gameEndedInSurrender:  True/False, indicating if the game is ended with one team surrendered before the winning condition is met
- teamEarlySurrendered: True/False
- visionScore: Numeric, indicating how much pro/counter-reconnaissance action player performed to get more map information for the team (may vary depends on role, support/jg commonly have higher vision score)
- timePlayed: Numeric, total time played in seconds

Other variables will not be considered as they cannot be determined during game prepare stage.
- totalDamagedDealt: Numeric, indicating total damage value dealt on opponent champions, minions and neutral entity
- totalDamageTaken: Numeric, indicating total damage value taken by the player champion
- totalHeal: Numeric, indicating total health point healed on players champion
- totalMinionsKilled: Numeric, indicating total opponent and neutral minions killed
- totalTimeCCDealt: Numeric, indicating total control (make enemy unable to attack for a period of time) time
- totalTimeSpentDead: 

## Loading the dataset
```{r}
# league_all_df <- read.csv("dataset/league_data_tail_10k_utf8.csv")
# league_all_df <- read.csv("dataset/league_data_10k_utf8.csv")

league_all_df <- vroom("dataset/league_data_utf8.csv")
# Drop all the irrelevant columns

```
```{r}
# Drop variables
league_all_df <- league_all_df %>%
    select(
        -c(summonerName,
        puuid,
        summonerId,
        ))
```

Give a list of variables and check for missing data
```{r}
head(league_all_df)
sum(is.na(league_all_df))
```


## Remove invalid games
Remake can be made under 3 minutes if one or more player is disconnected from the game in the first 1:30 minutes
- these game will not provide meaningful information to the model
- however, the game can still run for a period of time after remake voting is passed
- so to be safe, use 5 minutes as boundary
```{r}
league_all_df <- league_all_df %>%
    filter(timePlayed > 360)
dim(league_all_df)
```

## Conversion and Factor
Convert local time to the time of the day
```{r}
# Level: Morning (6-12), Afternoon(12-18), Evening(18-24), Midnight(0-6)



league_all_df <- league_all_df %>%
    mutate(
        Hour = strptime(league_all_df$KoreanTime, "%Y-%m-%d %H:%M:%S")$hour)


head(league_all_df$Hour,n = 20)
league_all_df <- league_all_df %>%
    mutate(TimeOfTheDay = case_when(
           between(Hour, 0, 6) ~ "PostMidnight",
           between(Hour, 7, 12) ~ "Morning",
           between(Hour, 13, 18) ~ "Afternoon",
           between(Hour, 18, 24) ~ "Evening",))

league_all_df <- league_all_df %>%
    mutate(team = case_when(
        teamId == "100" ~ "Blue",
        teamId == "200" ~ "Red",
    ))
```

```{r, warning=FALSE}
league_all_df_factored <- league_all_df %>%
    mutate(
        across(c(
            win,
            gameEndedInEarlySurrender,
            gameEndedInSurrender,
            teamEarlySurrendered),
        as.numeric))

league_all_df_factored <- league_all_df_factored %>%
    mutate(
        across(
            c(
                teamPosition,
                TimeOfTheDay,
                championName),
            as.factor)
    )
head(league_all_df_factored$TimeOfTheDay)

league_all_df_factored$TimeOfTheDay <- fct_relevel(
    league_all_df$TimeOfTheDay,
    c("PostMidnight", "Morning", "Afternoon", "Evening"))

league_all_df_factored$team <- fct_relevel(league_all_df$team, c("Blue", "Red"))
head(league_all_df_factored$Hour)
```

## Explore the distribution
```{r}
head(league_all_df_factored)
league_all_numeric <- league_all_df_factored %>%
    select(where(is.numeric)|where(is.factor)) %>%
    select(-c(gameNo,
    playerNo,
    participantId,
    teamId,
    unrealKills,
    teamEarlySurrendered,
    gameEndedInEarlySurrender))

league_all_numeric <- league_all_numeric %>%
    mutate(TimeOfTheDayN = as.numeric(TimeOfTheDay))

league_all_df_factored %>%
    filter(win == 1) %>%
    ggplot(aes(y = win, fill = team)) +
    geom_bar() +
    coord_polar() +
    scale_fill_manual(values=c("blue", "red")) +
    ggtitle("Team blue vs team red win rate")

head(league_all_numeric$Hour, n=20)
correlation <- league_all_numeric %>% correlate()
correlation %>%
  stretch() %>%
  ggplot(aes(x, y, fill = r)) +
  geom_tile() +
  geom_text(aes(label = as.character(fashion(r)))) +
  scale_fill_gradient2(low = "red", mid="white", high = "blue") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

# Logistic regression
```{r}
df_split <- initial_split(league_all_df_factored, prop = 0.7, strata = win)
league_train <- training(df_split)
league_testing <- testing(df_split)
```

```{r}
log_reg <- logistic_reg() %>%
    set_engine("glm")
    set_mode("classification")
```
